Board Game Recommendation

### 2015-03-02 paper.Rnw
couple of suggestions

There are two types of particular information that we will be interested in: user ratings of the games and characteristics about the game (referred to as classifiers in the modeling section). The characteristics we're interested in fall into these categories:

\begin{center}
\begin{tabular}{|l|c|}
\hline
Category &  This covers the broad categories a game\\
& might fall into (ex.: Humor, Puzzle, Sports, etc.) \\
\hline
Family &  Some games a naturally part of a "family" \\
&  that share a name or common element \\
& (ex.: Animals:Bats, Ancient Wars Series, Hello Kitty)\\
\hline
Mechanic &  This is what mechanisms the game uses\\
& (ex.: Dice Rolling, Card Drafting, Worker Placement)\\
\hline
Subdomain & More general than Category, but loosely bins games\\
& (ex.: Family Games, Strategy Games, etc.)\\
\hline
\end{tabular}
\end{center}

@@

@@

There are a few things that make sense to model first. Certain games are more popular than other games, and certain people will naturally be more or less generous than others in their ratings. These two effects are very important to measure, as the first will allow us to provide estimates for people that have rated no games (and therefore we know nothing about), and the second will allow us to fine tune estimates for people who have rated many games. We will implement these in the same way that BigChaos implemented the Global Effects model (page 6, BigChaos paper). While they implemented 14 steps, we will only use the 2, due to the complexity of the calculations required and the time with which it is practical to fit a model.

@@

Note for editing: I know this model is a mess at the moment, just getting the general ideas down on paper. 
\subsubsection{Global Effects}
The motivations for using the formulas that follow can be found in Scalable Collaborative Filtering with Jointly Derived Neighborhood Interpolation Weights (make this a bib reference). The general idea is to remove the global mean from all ratings to get a residual for each observation. We'll group these residuals by game, and then find an effect for that game. Subtracting this effect from the residual, we'll take those residuals and repeat the same for each user.

>>>>

There are two types of particular information that we will be interested in: user ratings of the games and characteristics about the game (referred to as classifiers in the modeling section). The characteristics we're interested in fall into these categories as outlined in table~\ref{tab:categories}

\hh{Just to make this flow better - make the table below an actual table in the table environment. Give it a caption and refer to it in the text ... I've just implemented it for you}
\begin{table}[ht]
\centering
\begin{tabular}{|l|c|}
\hline
Category &  This covers the broad categories a game\\
& might fall into (ex.: Humor, Puzzle, Sports, etc.) \\
\hline
Family &  Some games a naturally part of a "family" \\
&  that share a name or common element \\
& (ex.: Animals:Bats, Ancient Wars Series, Hello Kitty)\\
\hline
Mechanic &  This is what mechanisms the game uses\\
& (ex.: Dice Rolling, Card Drafting, Worker Placement)\\
\hline
Subdomain & More general than Category, but loosely bins games\\
& (ex.: Family Games, Strategy Games, etc.)\\
\hline
\end{tabular}
\caption{\label{tab:categories} Overview of the  relevant characteristics of board games considered in this project.}
\end{table}

@@

\hh{Give an example of how the data that you have scraped looks like. This would be a good point to introduce a bit of the notation that you are using below, like the $y_{u,i}$. }

\hh{Aren't you continuously scraping? You should mention this at this point, and also talk a bit about how you have implemented the scraping.}

@@

There are a few things that make sense to model first. Certain games are more popular than other games, and certain people will naturally be more or less generous than others in their ratings. These two effects are very important to measure, as the first will allow us to provide estimates for people that have rated no games (and therefore we know nothing about), and the second will allow us to fine tune estimates for people who have rated many games. We will implement these in the same way that BigChaos implemented the Global Effects model (page 6, BigChaos paper \hh{which of the BigChaos papers are you refering to here, exactly? At some point you need to include the exact reference in the bib tex, but I'd just like to know for myself ...}). While they implemented 14 steps, we will only use the 2 \hh{which 2? you need to include a few more details here}, due to the complexity of the calculations required and the time with which it is practical to fit a model.

@@

Note for editing: I know this model is a mess at the moment, just getting the general ideas down on paper. 
\hh{this is not nearly as messy as you make it out to be, but you need to make sure to define every little piece of notation as you, because otherwise your reader will be lost.}
\subsubsection{Global Effects}
The motivations for using the formulas that follow can be found in Scalable Collaborative Filtering with Jointly Derived Neighborhood Interpolation Weights (make this a bib reference). The general idea is to remove the global mean from all ratings to get a residual for each observation. We'll group these residuals by game, and then find an effect for that game. Subtracting this effect from the residual, we'll take those residuals and repeat the same for each user.
